Master Thesis

### 2013-06-12 the-last-part.tex
Added remark about "de" and NP_VAR
Brought back the "de" constraint to the E fragment"

While we have introduced the notion of an $NP\_VAR{=}T$ for describing
traces, we can cover another element of our fragment, the preposition
$de$, and enforce the constraint that $qui$/$que$ cannot extract
prepositional complements.

>>>>

While we have introduced the notion of an $NP\_VAR{=}T$ for describing
traces, we can cover another element of our running fragment, the
preposition $de$, and enforce the constraint that $qui$/$que$ cannot
extract prepositional complements by providing only a single type for
$de$ that accepts only unmoved noun phrases as complements.
